The \emph{FThresholds} package for \emph{Macaulay2}

### 2019-06-05 Fsing/FThresholdsPaper/FThresholds.tex

In this case, very roughly speaking, the {\tt fpt} function will either compute, and output, the exact value of the $F$-pure threshold of $f$, and otherwise recursively compute a finite sequence of upper and lower bounds for this value, and output the last of these, which will be the tightest among all computed.  The value of the option {\tt DepthOfSearch} determines the precision of the initial set of bounds, and the option {\tt Attempts}, in conjunction with some various subroutines, determines whether, and how, to produce new, tighter bounds from the previous ones.  %We note that a pair of bounds will be produced only if the exact value of the $F$-pure threshold remains undetermined.

In more detail, let $e$ denote the value of the option {\tt DepthofSearch}, which conservatively defaults to $1$.  The {\tt fpt} function first computes $\nu=\nu_f(p^e)$, which agrees with the output of {\tt nu(e,f)}.  It is well-known that the $F$-pure threshold of $f$ is greater than $\nu/p^e$ and at most $(\nu+1)/p^e$, and applying  {\color{red} \cite[Proposition 4.2]{}} to this lower bound tells us that the $F$-pure threshold of $f$ must be at least $\nu/(p^e-1)$.  In summary, we know that the $F$-pure threshold of $f$ must lie in the closed interval 
%
\begin{equation}
\label{estimating-interval: e}
\tag{$\dagger$}
\left[ \frac{\nu}{p^e-1}, \frac{\nu+1}{p^e} \right].
\end{equation}

With these estimates in hand, the subroutine {\tt guessFPT} is called to make some ``educated guesses" in an attempt to identify the $F$-pure threshold within this interval, or at least narrow down this interval to produce improved estimates.  The number of ``guesses" is controlled by the option {\tt Attempts}, which conservatively defaults to 3.  If {\tt Attempts} is set to 0, then {\tt guessFPT} is bypassed. If  {\tt Attempts} is set to at least 1, then a first check is run to verify whether the right-hand endpoint $(\nu+1)/p^e$ of the above interval \eqref{estimating-interval: e} the $F$-pure threshold.

 We illustrate this below.

>>>>

In this case, very roughly speaking, the {\tt fpt} function will either compute, and output, the exact value of the $F$-pure threshold of $f$, and otherwise recursively compute a finite sequence of lower and upper bounds for this value, and output the last of these, which will be the tightest among all computed.  The value of the option {\tt DepthOfSearch} determines the precision of the initial set of bounds, and the option {\tt Attempts}, in conjunction with some various subroutines, determines whether, and how, to produce new, tighter bounds from the previous ones.

In more detail, let $e$ denote the value of the option {\tt DepthofSearch}, which conservatively defaults to $1$.  The {\tt fpt} function first computes $\nu=\nu_f(p^e)$, which agrees with the output of {\tt nu(e,f)}.  It is well-known that the $F$-pure threshold of $f$ is greater than $\nu/p^e$ and at most $(\nu+1)/p^e$, and applying  \cite[Proposition 4.2]{HernandezFPurityOfHypersurfaces} to this lower bound tells us that the $F$-pure threshold of $f$ must be at least $\nu/(p^e-1)$.  In summary, we know that the $F$-pure threshold of $f$ must lie in the closed interval 
%
\begin{equation}
\label{estimating-interval: e}
\tag{$\dagger$}
\left[ \frac{\nu}{p^e-1}, \frac{\nu+1}{p^e} \right].
\end{equation}

With these estimates in hand, the subroutine {\tt guessFPT} is called to make some ``educated guesses" in an attempt to identify the $F$-pure threshold within this interval, or at least narrow down this interval to produce improved estimates.  The number of ``guesses" is controlled by the option {\tt Attempts}, which conservatively defaults to 3.  If {\tt Attempts} is set to 0, then {\tt guessFPT} is bypassed. If  {\tt Attempts} is set to at least 1, then a first check is run to verify whether the right-hand endpoint $(\nu+1)/p^e$ of the above interval \eqref{estimating-interval: e} the $F$-pure threshold.  We illustrate this below.
